Approximation as Differentiation: Notes

### 2025-06-05 main/approx-as-tangents.tex
edit the "Approximation as Tangents" section

For what follows we do not need to know in detail what a manifold is, or exactly how smooth functions are defined. We only state some definitions in order to fix terminology and to justify our claim of a connection to standard differentiablity. \bob{Need a good reference here.}

The general study of differentiable functions usually takes place on \emph{manifolds}, which are topological spaces that are ``locally'' like a Euclidean space $\RR^n$. The spaces $\RR^n$ are manifolds, but so are ``non-flat'' examples such as $n$-spheres and more exotic spaces. Every point $x$ in a manifold $M$ has an associated \emph{tangent vector space} $\tangents_x(M)$ and \emph{cotangent vector space} $\cotangents_x(M)$, the latter consisting of linear functions $\tangents_x(M) \linearto \RR$. The tangent and cotangent spaces are finite dimensional, so in the presence of a chosen basis they are canonically isomorphic. In the case when the manifold is $\RR^n$, then every tangent space is isomorphic to $\RR^n$ as well.

@@

Our thesis is that \GPS can profitably be seen as a form of differentiable programming, where tangents are not linear approximations of functions but instead are qualitiative approximations of elements in the sense of domain theory. Smooth functions in this setting are Berry's \emph{stable functions} in domain theory. We now introduce these concepts and how they relate to \GPS.

@@

Domain theory is a method for defining the semantics of programs that
handle infinite data (e.g., functions or infinite
streams). \emph{Domains} are special partially ordered sets where the
ordering denotes a relationship of qualitative information content: if
$x \sqsubseteq y$, then $y$ may contain more information than $x$. For
example, if $x$ and $y$ are functions, then $y$ may be defined at more
places in its domain than $x$. Infinite objects are understood in
terms of their approximations in this sense, and domains are assumed
to be closed under least upper bounds (lubs) of directed sets, meaning
that any internally consistent collection of elements has a
``completion'' that contains all the information covered by the
set. Programs are interpreted as monotone functions that preserve
directed lubs. The latter property is called continuity. Monoticity
captures the idea that if the input gets more defined, then the output
can get more defined. Continuity intuitively expresses the idea that a
function interpreting a program cannot ``look at all the
approximations'' when determining the output, which corresponds to the
intuitive idea that a computable function cannot look at a non-finite
amount of input to produce an output.

For the purposes of \GPS, we are not interested in using
approximations to model computation on infinite objects, but rather to
use them for the related task of revealing how programs explore their
inputs for provenance tracking. Therefore, in what follows we dispense with completeness properties of the partially ordered sets we consider.

@@

Continuous functions between domains capture the intuitive idea that
computable functions are restricted to finite observations of their
input for finite output. However, there are examples, such as
Plotkin's Parallel OR (\autoref{ex:parallel-or}, below) that are
continuous but do not treat their input in a way that is consistent
with a sequential implementation. Stability is an additional property
of monotone functions that was invented by Berry \cite{berry86} in an
attempt to capture sequentiality. This was not successful (see the
$\mathrm{gustave}$ function in \autoref{ex:parallel-or}), but we will
see now how it is closely related to problem of computing forward and
backwards maps of approximations needed in \GPS. A textbook
description of stable functions in the context of domain theory is
given by \citet{amadio-curien} (Chapter 12). We will
refer to this where necessary.

@@

\begin{definition}
  A \emph{bounded meet poset} is a partially ordered set $X$ where
  every for every $x \in X$, $\downset{x}$ is a meet semilattice, with
  $x$ as the top element.
\end{definition}

Smooth functions have a ``pushforward'' derivative that takes tangents
at a point $x$ to tangents at the point $f(x)$. In the partially
ordered setting, we require that the restriction of a monotone
function $f$ to each $\downset{x}$ preserves meets:

@@

\begin{example}[Conditionally Multiplicative Functions]
  To see the effect of requiring preservation of bounded meets,
  consider several ways of defining disjunction on the lifted booleans
  $\mathbb{B}_\bot$. Two functions that are cm are the strict and
  left-short-circuiting ORs\footnote{The clauses in these examples are
    shorthand for the graph of the function. They are not to be
    understood as pattern matching clauses in a language like Haskell,
    where it is not possible to match on $\bot$.}:
  \begin{displaymath}
    \begin{array}[t]{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{strictOr}&\mathsf{tt}&\mathsf{tt}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{tt}&\mathsf{ff}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{ff}&\mathsf{tt}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{ff}&\mathsf{ff}&=&\mathsf{ff} \\
      \mathrm{strictOr}&\bot&\_&=&\bot \\
      \mathrm{strictOr}&\_&\bot&=&\bot \\
    \end{array}
    \qquad
    \begin{array}[t]{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{shortCircuitOR}&\mathsf{tt}&\_&=&\mathsf{tt} \\
      \mathsf{shortCircuitOR}&\mathsf{ff}&x&=&x \\
      \mathsf{shortCircuitOR}&\bot&\_& =& \bot
    \end{array}
  \end{displaymath}
  \bob{Demonstrate that they are conditionally multiplicative, by
    giving evidence of stability and stating that this implies cm}

  The function $\mathrm{strictOr}$ is stable. For example, for the
  input-output pair $(\mathsf{tt},\mathsf{ff}), \mathsf{tt}$, the
  minimal input that gives this output is exactly
  $(\mathsf{tt}, \mathsf{ff})$. If we take the approximation
  $\bot \leq \mathsf{tt}$ of the output, then the corresponding
  minimal input is $(\bot, \bot)$. The function
  $\mathrm{shortCircuitOR}$ is also stable. For the input-output pair
  $(\mathsf{tt},\mathsf{ff}),\mathsf{tt}$, the minimal input that
  gives this input is $(\mathsf{tt},\bot)$, indicating that the
  presence of $\mathsf{ff}$ in the second argument was not necessary
  to produce this output. As with $\mathrm{strictOr}$, the minimal
  input required to produce the output $\bot \leq \mathsf{tt}$ is
  again $(\bot,\bot)$.

  The fact that these two functions's stability witnesses reveal
  information about how they depend on their input is what we will
  exploit in order to use the idea of stability for slicing.
\end{example}

\begin{example}[A non-Conditionally Multiplicative Function]
  \label{ex:parallel-or}
  A function that is not cm is Plotkin's Parallel OR \cite{lcf77},
  which short-circuits in both arguments, returning $\mathsf{tt}$ if
  either argment is $\mathsf{tt}$, even if the other argument is not
  defined:
  \begin{displaymath}
    \begin{array}{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{parallelOR}&\mathsf{tt}&\_&=&\mathsf{tt} \\
      \mathrm{parallelOR}&\_&\mathsf{tt}&=&\mathsf{tt} \\
      \mathsf{parallelOR}&\mathsf{ff}&\mathsf{ff}&=&\mathsf{ff} \\
      \mathsf{parallelOR}&\bot&\bot&=&\bot
    \end{array}
  \end{displaymath}
  For the input-output pair $(\mathsf{tt},\mathsf{tt}),\mathsf{tt}$,
  there is no one minimal input that produces this output. We have
  both $\mathrm{parallelOR}(\mathsf{tt},\bot) = \mathsf{tt}$ and
  $\mathrm{parallelOR}(\bot,\mathsf{tt}) = \mathsf{tt}$, which are
  incomparable and their greatest lower bound $(\bot,\bot)$ gives the
  output $\bot$.

  Parallel OR is famous because it is not \emph{sequential}, meaning
  intuitively that it cannot be implemented without running the two
  arguments in parallel to see if one of them returns
  $\mathsf{tt}$. That fact that it exists in the standard domain
  theoretic semantics of PCF means that this semantics is complete for
  reasoning about observational equivalence in PCF. Since Parallel OR
  is not stable, one might hope that stability is enough to capture
  sequentiality, and hence potentially give a fully abstract model of
  PCF. However, the following ternary function
  $\mathbb{B}_\bot^3 \to \{\top,\bot\}$ is stable but admits no
  sequential implementation that fixes an order that the arguments are
  examined in:
  \begin{displaymath}
    \begin{array}{l@{(}l@{,~}l@{,~}l@{)~}c@{~}l}
      \mathrm{gustave}&\mathsf{tt}&\mathsf{ff}&\_&=&\top \\
      \mathrm{gustave}&\mathsf{ff}&\_&\mathsf{tt}&=&\top \\
      \mathrm{gustave}&\_&\mathsf{tt}&\mathsf{ff}&=&\top \\
      \mathrm{gustave}&\_&\_&\_&=&\bot
    \end{array}
  \end{displaymath}
  Despite there being no one minimal input that achieves the output
  $\top$, each of the minimal inputs that can achieve this output are
  pairwise incomparable, so for each specific input that gets output
  $\top$ there is a unique minimal input that achieves it (listed in
  the first three lines of the definition).

  In terms of \GPS the $\mathrm{gustave}$ function does not present a
  problem. For any particular run (i.e., input-output pair) of the
  program, there is an unambiguous minimal input that achieves the
  output, no matter that it was not achieved by a sequential
  processing of the input.
\end{example}

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  In the preceeding examples, we demonstrated conditional
  multiplicativity by giving a backwards mapping of approximations
  that forces preservation of meets. A natural question is whether or
  not we always have such a backwards map which we could use for
  backwards propagation of approximations. An example that is
  conditionally multiplicative, but does not admit such a backards map
  (from Amadio and Curien just before Lemma 12.2.3, originally due to
  Berry) is given by defining
  $\mathrm{unstable} : D \to \{\bot, \top\}$, where:
  \begin{displaymath}
    D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots \sqsubseteq 1 \sqsubseteq 0
  \end{displaymath}
  as $\mathrm{unstable}(\bot) = \bot$ and
  $\mathrm{unstable}(n) = \top$. This is monotone, and preserves meets
  in every $\downset{x}$. However, there is no ``best'' (i.e., least)
  input that gives us any finite output.
\end{example}

In light of the preceeding example, we can give an alternative
definition of a function that requires the existence of a reverse
mapping directly, without assuming that any meets exist:

@@

\begin{example}
  \bob{Elaborate on the examples}
  \begin{enumerate}
  \item $\mathrm{strictOr}$ and $\mathrm{shortCircuitOR}$ are stable, as demonstrated above.
  \item $\mathrm{parallelOR}$ is not stable.
  \item $\mathrm{gustave}$ is stable.
  \item $\mathrm{unstable}$ is not stable, but is conditionally multiplicative.
  \end{enumerate}
\end{example}

@@

We now summarise the analogy between differentiable functions between manifolds and stable functions between L-posets:

@@

>>>>

% For what follows we do not need to know in detail what a manifold is, or exactly how smooth functions are defined. We only state some definitions in order to fix terminology and to justify our claim of a connection to manifolds and smooth functions. \bob{Need a good reference here.}

The general study of differentiable functions takes place on \emph{manifolds}, which are topological spaces that ``locally'' look like a subset of the Euclidean space $\RR^n$. The spaces $\RR^n$ themselves are manifolds, but so are ``non-flat'' examples such as $n$-spheres and yet more exotic spaces. Every point $x$ in a manifold $M$ has an associated \emph{tangent vector space} $\tangents_x(M)$ and \emph{cotangent vector space} $\cotangents_x(M)$, the latter consisting of linear functions $\tangents_x(M) \linearto \RR$. The tangent and cotangent spaces are finite dimensional, so in the presence of a chosen basis they are canonically isomorphic. In the case when the manifold is $\RR^n$, then every tangent space is isomorphic to $\RR^n$ as well.

@@

Our thesis is that \GPS is a form of differentiable programming, where tangents are not linear approximations of functions but instead are qualitiative approximations of elements in the sense of domain theory. Smooth functions in this setting are Berry's \emph{stable functions} \cite{berry}. We now introduce these concepts and how they relate to \GPS.

@@

Domain theory is a method for defining the semantics of programs that handle infinite data (e.g., functions or infinite streams). \emph{Domains} are certain partially ordered sets where the ordering denotes a relationship of qualitative information content: if $x \sqsubseteq y$, then $y$ may contain more information than $x$. For example, if $x$ and $y$ are functions, then $y$ may be defined for more values in its domain than $x$. Infinite objects are understood in terms of their approximations in this sense, and domains are assumed to be closed under least upper bounds (lubs) of directed sets, meaning that any internally consistent collection of elements has a ``completion'' that contains all the information covered by the set. Programs are interpreted as monotone functions that preserve directed lubs. Monotonicity captures the idea that if the input gets more defined, then the output can get more defined. Preservation of lubs, or \emph{continuity}, states that a function interpreting a program cannot act inconsistently on approximations and their completion, which corresponds to the intuitive idea that a function that is computable cannot look at a non-finite amount of input to produce a finite output.

For the purposes of \GPS, we are not interested in using approximations to model computation on infinite objects, but instead to use them for the related use of revealing how programs explore their inputs when producing parts of their output. Therefore, we ignore completeness properties of the partially ordered sets we consider.

@@

%FIXME: use cleverref

When giving a denotational semantics for sequential programming languages, such as PCF, continuous functions are too permissive. Plotkin's Parallel OR (\autoref{ex:parallel-or}, below) is continuous but does not treat its input in a way that is consistent with a sequential implementation \cite{plotkin77lcf}. Continuous functions can explore their input in a ``random access'' way, which is incompatible with the central idea in \GPS that we should be able to identify a \emph{minimal} part of the input that leads to a part of the output.

Stability is a property that can be required of monotone functions that was invented by Berry \cite{berry86} in an attempt to capture sequentiality. This was not successful (see the $\mathrm{gustave}$ function in \autoref{ex:parallel-or}), but we will see now how it is closely related to problem of computing forward and backwards maps of approximations needed in \GPS. A textbook description of stable functions in the context of domain theory is given by \citet{amadio-curien} (Chapter 12). We start with a property that is weaker than stability, but is easier to motivate in connection with derivatives of smooth functions.

@@

\begin{definition}
  A \emph{bounded meet poset} is a partially ordered set $X$ where for every $x \in X$, $\downset{x}$ is a meet semilattice, with $x$ as the top element.
\end{definition}

Smooth functions have a ``pushforward'' derivative that takes tangents at a point $x$ to tangents at the point $f(x)$ and is linear. In the partially ordered setting, we are going to take a function $f$'s pushforward derivative at $x$ to be its restriction to $\downset{x}$, taking approximations of the input to approximations of the output. Matching the linearity of the pushforward derivative smooth functions, we require that these restrictions preserve meets:

@@

\begin{example}[Conditionally Multiplicative Functions]
  To see the effect of requiring preservation of bounded meets,
  consider several ways of defining disjunction on the lifted booleans
  $\mathbb{B}_\bot$. Two functions that are cm are the strict and
  left-short-circuiting ORs\footnote{The clauses in these examples are
    shorthand for the graph of the function. They are not to be
    understood as pattern matching clauses in a language like Haskell,
    where it is not possible to match on $\bot$.}:
  \begin{displaymath}
    \begin{array}[t]{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{strictOr}&\mathsf{tt}&\mathsf{tt}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{tt}&\mathsf{ff}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{ff}&\mathsf{tt}&=&\mathsf{tt} \\
      \mathrm{strictOr}&\mathsf{ff}&\mathsf{ff}&=&\mathsf{ff} \\
      \mathrm{strictOr}&\bot&\_&=&\bot \\
      \mathrm{strictOr}&\_&\bot&=&\bot \\
    \end{array}
    \qquad
    \begin{array}[t]{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{shortCircuitOR}&\mathsf{tt}&\_&=&\mathsf{tt} \\
      \mathsf{shortCircuitOR}&\mathsf{ff}&x&=&x \\
      \mathsf{shortCircuitOR}&\bot&\_& =& \bot
    \end{array}
    \qquad
    \raisebox{-15ex}{
      \begin{tikzpicture}
        \node (top) at (0,0) {$(\mathsf{tt},\mathsf{ff})$};
        \node [below of=top,xshift=-0.5cm] (oi) {$(\bot,\mathsf{ff})$};
        \node [below of=top,xshift=0.5cm] (io) {$(\mathsf{tt},\bot)$};
        \node [below of=oi,xshift=0.5cm] (oo) {$(\bot,\bot)$};
        \draw (top) -- (oi);
        \draw (top) -- (io);
        \draw (oi) -- (oo);
        \draw (io) -- (oo);
      \end{tikzpicture}
    }
  \end{displaymath}
  In the poset $\mathbb{B}_\bot^2$, a typical poset of approximations of a fully defined element is shown to the right. For $\mathrm{strictOr}$, any approximation that isn't the fully defined input is mapped to $\bot$, while $\mathrm{shortCircuitOr}$ maps the partially defined $(\mathsf{tt},\bot)$ to $\mathsf{tt}$. Thus, even though these functions operate identically on fully defined inputs, they differ in their \emph{derivatives} on partially defined input, exposing how . That they are cm can be checked by examining their restrictions' behaviour. If we take the approximations $(\bot,\mathsf{ff})$ and $(\mathsf{tt},\bot)$, then their meet is $(\bot,\bot)$; $\mathrm{strictOr}$ maps all three elements to $\bot$, so is cm here since $\bot \wedge \bot = \bot$; and $\mathrm{shortCircuitOR}$ has $(\bot,\mathsf{ff}) \mapsto \bot$ and $(\mathsf{tt},\bot) \mapsto \mathsf{tt}$, the meet of which is $\bot = \mathrm{shortCircuitOR}(\bot,\bot)$. Other combinations can be checked similarly.
\end{example}

\begin{example}[A non-Conditionally Multiplicative Function]
  \label{ex:parallel-or}
  A function that is not cm is Plotkin's Parallel OR \cite{lcf77}, which short-circuits in both arguments. It returns $\mathsf{tt}$ if either argment is $\mathsf{tt}$ even if the other argument is not defined:
  \begin{displaymath}
    \begin{array}{l@{(}l@{,~}l@{)~}c@{~}l}
      \mathrm{parallelOR}&\mathsf{tt}&\_&=&\mathsf{tt} \\
      \mathrm{parallelOR}&\_&\mathsf{tt}&=&\mathsf{tt} \\
      \mathsf{parallelOR}&\mathsf{ff}&\mathsf{ff}&=&\mathsf{ff} \\
      \mathsf{parallelOR}&\bot&\bot&=&\bot
    \end{array}
  \end{displaymath}
  We have $\mathrm{parallelOR}(\mathsf{tt}, \bot) \wedge \mathrm{parallelOR}(\bot, \mathsf{tt}) = \mathsf{tt} \wedge \mathsf{tt} = \mathsf{tt}$ but $\mathrm{parallelOR}((\mathsf{tt},\bot) \wedge (\bot, \mathsf{tt})) = \mathrm{parallelOR}(\bot, \bot) = \bot$, so it is not cm.

  Parallel OR is famous because it is not \emph{sequential}, meaning intuitively that it cannot be implemented without running the two arguments in parallel to see if one of them returns $\mathsf{tt}$. The fact that it exists in the standard domain theoretic semantics of PCF means that this semantics is incomplete for reasoning about observational equivalence in PCF. Since Parallel OR is not cm, one might hope that cm-ness is enough to capture sequentiality, and hence potentially give a fully abstract model of PCF. However, the following ternary function $\mathbb{B}_\bot^3 \to \{\top,\bot\}$ is cm but admits no sequential implementation that fixes an order that the arguments are examined in:
  \begin{displaymath}
    \begin{array}{l@{(}l@{,~}l@{,~}l@{)~}c@{~}l}
      \mathrm{gustave}&\mathsf{tt}&\mathsf{ff}&\_&=&\top \\
      \mathrm{gustave}&\mathsf{ff}&\_&\mathsf{tt}&=&\top \\
      \mathrm{gustave}&\_&\mathsf{tt}&\mathsf{ff}&=&\top \\
      \mathrm{gustave}&\_&\_&\_&=&\bot
    \end{array}
  \end{displaymath}
  Due to the way that the cases are defined, there is no way of constructing a pair of approximations for which preservation of their meet does not hold. In terms of derivatives, this makes sense in that we are only concerned about the intensional behaviour of a function at a point and its approximations. Parallel OR has two incompatible approximation behaviours at the point $(\mathsf{tt},\mathsf{tt})$. The $\mathrm{gustave}$ function does have consistent behaviour at each approximation for each point.

%  \bob{What have hyperstable functions?}
\end{example}

Conditional multiplicativity seems to be a reasonable analogue to functions with a well-defined notion of derivative. However, for \GPS we also require an analogue to the reverse derivative, where we map approximations backwards to give the least approximation of the input for a given approximation of the output. In the case of smooth functions, we are always guaranteed a reverse derivative but there is not always a best way to map approximations backwards for cm functions, as the following example shows.

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  % In the preceeding examples, we demonstrated conditional
  % multiplicativity by giving a backwards mapping of approximations
  % that forces preservation of meets. A natural question is whether or
  % not we always have such a backwards map which we could use for
  % backwards propagation of approximations.
  An example that is conditionally multiplicative, but does not admit a backards map of approximations (from \citet{amadio-curien} just before Lemma 12.2.3, originally due to Berry) is given by defining $\mathrm{unstable} : D \to \{\bot, \top\}$, where:
  \begin{displaymath}
    D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots \sqsubseteq 1 \sqsubseteq 0
  \end{displaymath}
  as $\mathrm{unstable}(\bot) = \bot$ and $\mathrm{unstable}(n) = \top$. This is monotone, and preserves meets in every $\downset{x}$. However, there is no ``best'' (i.e., least) input that gives us any finite output.
\end{example}

In light of the preceeding example, we can give an alternative
definition of a function that requires the existence of a reverse
mapping directly, even without assuming that any meets exist:

@@

\begin{example}
  \begin{enumerate}
  \item The function $\mathrm{strictOr}$ is stable. For example, for the input-output pair $(\mathsf{tt},\mathsf{ff}) \mapsto \mathsf{tt}$, the minimal input that gives this output is exactly $(\mathsf{tt}, \mathsf{ff})$. If we take the approximation $\bot \leq \mathsf{tt}$ of the output, then the corresponding minimal input is $(\bot, \bot)$. The function $\mathrm{shortCircuitOR}$ is also stable. For the input-output pair $(\mathsf{tt},\mathsf{ff}) \mapsto \mathsf{tt}$, the minimal input that gives this input is $(\mathsf{tt},\bot)$, indicating that the presence of $\mathsf{ff}$ in the second argument was not necessary to produce this output. As with $\mathrm{strictOr}$, the minimal input required to produce the output $\bot \leq \mathsf{tt}$ is again $(\bot,\bot)$.

  \item The $\mathrm{parallelOR}$ function is not stable. For the input-output pair $(\mathsf{tt},\mathsf{tt}) \mapsto \mathsf{tt}$, there is no one minimal input that produces this output. We have both $\mathrm{parallelOR}(\mathsf{tt},\bot) = \mathsf{tt}$ and $\mathrm{parallelOR}(\bot,\mathsf{tt}) = \mathsf{tt}$, which are incomparable and their greatest lower bound $(\bot,\bot)$ gives the output $\bot$.

  \item The $\mathrm{gustave}$ function is stable. Despite there being no one minimal input that achieves the output $\top$, each of the minimal inputs that can achieve this output are pairwise incomparable, so for each specific input that gets output $\top$ there is a unique minimal input that achieves it (listed in the first three lines of the definition).

    In terms of \GPS the $\mathrm{gustave}$ function does not present a problem. For any particular run (i.e., input-output pair) of the program, there is an unambiguous minimal input that achieves the output, no matter that it was not achieved by a sequential processing of the input.

  \item As discussed above, $\mathrm{unstable}$ is not stable, but is conditionally multiplicative.
  \end{enumerate}
\end{example}

The fact that these two functions's stability witnesses reveal information about how they depend on their input is what we will exploit in order to use the idea of stability for \GPS. It is interesting that sequentiality is not necessarily required in order to obtain backwards maps of approximations, as might be assumed by thinking about how to trace computations for provenance information.

@@

We now summarise our analogy between differentiable functions between manifolds and stable functions between L-posets:

@@

\bob{Put a conjecture about Tangent Categories in somewhere}
